---
title: "Project Proposal"
output:
     html_document
---

__Proposal Deadline: Feb 3, 2019 23:59:00 hrs.__

- Edit this markdown file by __replacing only__ what is there in the
chunks named `q0`, `q1`, `q2`, ..., `q5` with your team's appropriate
answers. These chunks have been filled in as an example using the
OpenFDA data.

- Upload the filled in markdown to the project proposal assignment
area (will be created shortly) in every one of the team member's
private directory with the name `proposal.Rmd`.

0. Who are the authors of this package? See format below where you
   should replace `sunet1`, `sunet2`, and `Full Name1` and `Full
   Name2`.

```{r q0}
authors <- list(sunet1 = "Tianjiang Wang",
                sunet2 = "Qinbo Qu")
```

1. What is your package trying to achieve?  Who is it aimed at?

```q1

1)  Visualization.  The package will visualize local weather data,
particularly to compare data at nearby sites to show microclimate patterns.

2)  Analysis.  It will also include three functions to analyze
    1) Retrieve zip code from place name  
    2) Find nearby populated cities 
3)  other


The package is to make the quality weather information available to people in U.S.

```

2. Briefly describe the background if that's not obvious.  What field
   or area of interest is it related to?  (Just briefly, in a paragraph
   or two, maximum.) References, including web references, are welcome
   where available.
   
```q2

This package design is inspired by personal Weather underground
A link to the website is
here

https://www.wunderground.com/

Personal weather station is very wide in scope, and we will narrow it down as
below:

1) The project will focus on a couple of geo locations
2) Will test two statistical methods for predictor importance.
```

3. Provide one or two use cases; that is, in a sentence or so say how
   you see someone using the package.

```q3

People will query the R package for local weather information. The queries
will allow them to input person information.

People can also visualize the results of their queries.

People will also be able to utilize the analytical functions to
weather forecast.

Administrative organizations will query the R package for microclimate
patterns in order to monitor the polution condition.These queries can
also be parameterized by the user.

```

4. If you can, list the main functions or other software you plan on
   including.  No need to implement anything now, but you should have
   an idea.

```q4

The R package will provide the following functions: reading and
writing data, creating graphs and visualizations, running
parameterized queries against datasets, providing for download
capabilibities of both data and graphics.  The R package will also
provide functions for deep analysis by the user.

```

```{r, echo = FALSE, hide = FALSE}
## Do not edit
none <- "none"
basic <- "basic"
proficient <- "proficient"
dangerous <- "dangerous :-)"
```

5. For languages C/C++, Java, Python, Ruby, please specify your
   proficiency: Proficient, basic knowledge, no knowledge.  (This
   helps us evaluate the proposal sometimes and offer suggestions.)

```{r q5}
languages <- list(
    ## replace the sunet1 and sunet2 as you did above and edit
    ## appropriately for each member
    sunet1 = c(cxx = none,
               java = none,
               python = basic,
               julia = none, 
               ruby = none)
    ,
    sunet2 = c(cxx = none,
               java = none,
               python = basic,
               julia = none,                
               ruby = none)
)
```








