---
title: "Stat290 finalproject"
author: "Tianjiang Wang; Qinbo Qu"
date: "`r Sys.Date()`"
output: html_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This project shows a local weather pattern in SF Bay area using 2018 personal weather stations data from WU. 

1) provide interactive way for user to select city/geo location and show weather pattern
2) show local area weather pattern
    i)   Temperature (mean/min/max) 
    ii)  Humidity (mean/min/max)
    iii) Wind (direction/speed)
    iv)  Temperature contour line
    v)   Weather historical trend
    vi)  user data save/reload in Shiny UI


```{r stat290 finalproject}
#' @return run package
library(stat290.finalproject)
#' run shiny UI as below: 
#' runWeatherUI()
```


```{r history_weather}
#' @return a table of historical weather for selected city
#' ?history_weather
c="Alameda"
d1="2018-06-01"
d2="2018-12-31"
history_weather_tbl=history_weather(city_name = c,start_date=d1,end_date=d2)
history_weather_tbl[1:3,]

```


```{r nearby_pws_city}
#' @return a table of historical weather of nearby stations(PWS) based on selected city

#' ?nearby_pws_city
pws_id_selected <- nearby_pws_city(city_name = "Alameda",check_date="2018-05-05")
pws_id_selected[1:3,]

```


notes
```{r nearby_pws_coordinates}
#' @return a table of historical weather of nearby stations(PWS) based on location (lon,lat and distance(meter))

#' ?nearby_pws_coordinates
l1=-122.27999878
l2=37.52000046
dis=4000
d="2018-05-05"
pws_id_selected=nearby_pws_coordinates(lon=l1,lat=l2,distance = dis,data=pws,check_date = d)
pws_id_selected[1:3,]
```

```{r weather_map}
#' @return a map of historical weather for selected PWS list or city
#' ?weather_map
library(ggplot2)
library(ggmap)
library(akima)
pws_id_selected <- nearby_pws_city(city_name = "Alameda",check_date="2018-05-05")
weather_map(df=pws_id_selected)
pws_id_selected <- nearby_pws_city(city_name = "Belmont",check_date="2018-05-05")
weather_map(df=pws_id_selected)

```


```{r history_temp_daily}
#' @return a chart of historical daily tempature with mean, max and min values

#' ?history_temp_daily
d1="2018-06-01"
d2="2018-12-31"
city="Alameda"
history_weather_tbl=history_weather(city_name = city,start_date=d1,end_date=d2)
history_temp_daily(df=history_weather_tbl)

```

```{r history_temp_month}
#' @return a chart of historical month tempature with mean, max and min values

#' ?history_temp_month
d1="2018-06-01"
d2="2018-12-31"
city="Alameda"
history_weather_tbl=history_weather(city_name = city,start_date=d1,end_date=d2)
history_temp_month(df=history_weather_tbl)

```
```{r history_humidity_daily}
#' @return a chart of historical daily humidity with mean, max and min values

#' ?history_humidity_daily
d1="2018-06-01"
d2="2018-12-31"
city="Alameda"
history_weather_tbl=history_weather(city_name = city,start_date=d1,end_date=d2)
history_humidity_daily(df=history_weather_tbl)

```


```{r history_humidity_month}
#' @return a chart of historical monthly humidity with mean, max and min values

#' ?history_humidity_month
d1="2018-06-01"
d2="2018-12-31"
city="Alameda"
history_weather_tbl=history_weather(city_name = city,start_date=d1,end_date=d2)
history_humidity_month(df=history_weather_tbl)

```

```{r weather_windrose}
#' @return a wind rose

#' ?weather_windrose
df=history_weather(city_name = "Alameda",start_date="2018-06-01",end_date="2018-12-31")
weather_windrose(data = df, spd = "wind_speed", dir = "wind_dir_degrees")

```

```{r shiny UI}
#' @return shiny UI
#' run shiny UI as below: 
library(gridExtra)
library(ggmap)
#runWeatherUI()
```
